Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Remaining event types

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of speech \citep{hausler2021studyforrest} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of (concrete and countable) nouns that
the narrator uses to describe the movie's missing visual content based on a set
of rules.
% preliminary annotation
A preliminary annotation was performed by one person according to the rules.
% corrections
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, the rule for a word to belong to
a category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (cf. Table \ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
\texttt{body} & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{geo-room} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the movie stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square energy averaged across the length of every movie frame
(\unit[40]{ms}).

>>>>

% AD annotation
For the analysis of the audio-description stimulus, we extended a publicly available annotation
of its speech content \citep{hausler2021studyforrest} by classifying
concrete and countable nouns that the narrator uses to describe the movie's absent visual content.
% annotation procedure
An initial annotation was performed by one individual,
% corrections
and minor corrections were applied after comparing with a second categorization
done by the author.
% reference to table with rules and examples
A complete overview of all 18 noun categories, their inclusion criteria, and examples
can be seen in Table \ref{tab:descr-nouns-rules}.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
The categories \texttt{setting\_new} and \texttt{setting\_rec} comprise not just
words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in a]
disco'', ``[the platoon wades through a] rice field''). They also comprise words
that could count as a member of another category in case the narrator uses
these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').
% how it was handled
These nouns were flagged with both categories during the initial annotation
procedure. In context of the current analyses these word are considered to
belong exclusively to the higher-level category of changing a setting
(\texttt{se\_new} or \texttt{se\_old}).
% pooling of categories
Some noun categories that were semantically similar and offered only a small
amount of counts were pooled resulting in 11 final event categories (see Table
\ref{tab:ao-events}). These event categories were then used to model hemodynamic
responses.

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the nouns spoken by
        the audio-description's narrator.
        Examples are given in English.
        Some of these initial 18 noun categories were pooled resulting in 11
        event categories that served as basis to build the regressors of the
        GLM
        (cf. Table \ref{tab:ao-events}).
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lp{61mm}p{61mm}}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
\texttt{body} & trunk of the body; possibly clothed & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
\texttt{bodypart} & limbs & arm, finger, leg, toe
\tabularnewline
\texttt{face} & face or parts of it & face, ear, nose, mouth
\tabularnewline
\texttt{female} & female person & nurse, mother, woman
\tabularnewline
\texttt{females} & female persons & women
\tabularnewline
\texttt{fname} & female name & Jenny
\tabularnewline
\texttt{furniture} & movable furniture (insides \& outsides) & bench, bed, table, chair
\tabularnewline
\texttt{geo} & immobile landmarks & building, tree, street, alley, meadow, cornfield
\tabularnewline
\texttt{geo-room} & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
\texttt{head} & non-face parts of the head; worn headgear & head, hair, ear, neck;
helmet
\tabularnewline
\texttt{male} & male person & man, father, soldier
\tabularnewline
\texttt{males} & male persons & boys, opponents
\tabularnewline
\texttt{mname} & male name & Bubba, Kennedy
\tabularnewline
\texttt{object} & countable entity with firm boundaries & telephone, car
\tabularnewline
\texttt{objects} & countable entities & wheels, plants
\tabularnewline
\texttt{persons} & concrete persons of unknown sex & hippies, patients
\tabularnewline
\texttt{setting\_new} & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
\texttt{setting\_rec} & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

% low-leve confounds: intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the movie stimulus, we computed the mean luminance (arbitrary units,
average pixel brightness) of a movie frame (\unit[40]{ms}), the difference in
mean luminance of each frame's left and right half, the difference in mean
luminance of the lower and upper half.  As an indiciator of visual change, we
compute perceptual fingerprints for each movie frame using the pHash library
\todo{cite Zauner, Christoph: Implementation and Benchmarking of Perceptual
Image Hash Functions. Master's thesis, Upper Austria University of Applied
Sciences, Hagenberg Campus, 2010.} and recorded the commulative bitwise
difference to the previous frame.
% auditory shit
Finally for both audio tracks, we computed the left-right difference in volume
and root mean square energy averaged across the length of every movie frame
(\unit[40]{ms}).
